### 2023-11-13 paper.tex
Added rough crude prevalence section

@@

>>>>

\subsection{Calculating Crudge Prevalence Rate}

@@

Using this analytical approach, tabulation can be quickly conducted across patients.
Additionally, throughout the process, one can perform relevant analysis methods.
Here, we'll conduct a crude prevalence calculation across the patient cohort.

As seen in Table 1 and Table 2, informative results can be rapidly generated by this workflow relevant to observational health research.
Although the values shown in Table 2 are synthetic and the crude prevalence values themselves are meaningless, we can take a this approach and apply it directly to the MIMIC III dataset.
In Table 3, we can calculate across this dataset meaningful statistics that could later be further analyzed and drive further questioning (such as ...).
